
The research detailed in this document is the result of a collaborative effort in the ATLAS experiment.
In parallel, a clear description of the work requires an account of all sectors involved in the analyses,
even the ones in which the author did not contribute directly.
The list below is presented to clarify the author's contribution in each chapter.

\begin{itemize}
  \item Chapter~\ref{chp:bjet}: The author contributed the data to simulation comparison plots, which were used in the ATLAS Collaboration, to perform a recalibration of the \bjet trigger taggers.
  \item Chapter~\ref{chp:ttbarjets}: The author performed the data to simulation comparison at reconstruction level, including a calculation of all systematic uncertainty effects, all the Monte Carlo simulation backgrounds and the implementation of the correction factors (but not including the data-driven background parametrisation estimates for the $W$ + jets and QCD multi-jets backgrounds); the full unfolding procedure described, calculating all the correction factors from simulation; the propagation of systematic uncertainties through the unfolding procedure; the final unfolded data to particle-level simulaton comparison.
  \item Chapter~\ref{chp:ttbarres7}: The author contributed the data to simulation comparison estimates, including all systematic effect estimates and all Monte Carlo simulation background estimates (but not the $W$ + jets and QCD multi-jets backgrounds' parametrisation estimate).
  \item Chapter~\ref{chp:ttbarres8}: The author contributed the data to simulation comparison estimates, including all systematic effects estimates and all Monte Carlo simulation background estimates (but not the $W$ + jets data-driven parametrisation estimate). The author also contributed in the QCD multi-jets background parametrisation and estimation in this analysis.
\end{itemize}

